---
title: "BiocRevSumm: overviews of packages in review at Bioconductor"
shorttitle: "outlier dytection methods"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{BiocRevSumm: overviews of packages in review at Bioconductor}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---


# Introduction

The BiocRevSumm package includes tooling to 
survey issues in the Bioconductor contributions repositories
with the aim of producing a structured summary of package objectives
and capabilities.

# Tools for exploring packages under review

## Enumerating packages in review

```{r geto, message=FALSE}
library(BiocRevSumm)
iss = get_repos_from_open_issues("bioconductor", "contributions")
head(iss)
```

## Finding the vignettes for high-resolution categorization

```{r getv}
lk1 = strsplit(iss, "\\/")[[1]]
ghuser = lk1[4]
ghrepo = lk1[5]
lkvigs = list_github_dir(user = ghuser, repo = ghrepo, path="vignettes") 
vigs = grep("rmd|Rmd|Rnw|rnw", lkvigs, value=TRUE)
url = build_vignette_path(ghuser, ghrepo, branch="main", vname=vigs[1])
url
```

## Summarize a selected vignette

The summarization prompts are in the source code of `vig2data`.

```{r dosumm}
ans = vig2data(url)
writeLines(strwrap(ans$focused, 75))
```

# Summaries for packages in review on 22 Nov 2025


```{r res, results="asis", echo=FALSE}
library(BiocRevSumm)
data("viglist_23_nov_2025", package="BiocRevSumm")
url2heading = function(x) {
 stopifnot(length(x)==1)
 z = strsplit(x, "\\/")[[1]]
 sprintf('\n\n## Package %s from repo %s ([repo link](https://github.com/%s/%s))\n\n', z[5], z[4], z[4], z[5])
 }
for (i in seq_len(length(viglist_23_nov_2025))) {
 curvig = viglist_23_nov_2025[[i]]
 cat(url2heading(curvig), "\n")
 Sys.sleep(15)
 ans = vig2data( curvig )
 z = strsplit(curvig, "\\/")[[1]]
 fn = sprintf("%s_%s.rds", z[4], z[5])
 saveRDS(ans, file=fn)
 foc = ans$focused
# foc = gsub("#", "\n\n##", foc)
 cat(foc)
}
```
